Output Summary

### 2023-04-20 03-post-process/output-plots-children/06-length-based-survival.Rmd

## Parr $\to$ Smolt Overwinter Survival

```{r overwinter-survival-plots, fig.width = 8, fig.height = 5}
plot_fn = function(j, i) {

@@

  # realized pairs
  segments(L_Pb_lwr, phi_Pa_Mb_mean, L_Pb_upr, phi_Pa_Mb_mean, col = alpha("red", 0.5))
  segments(L_Pb_mean, phi_Pa_Mb_lwr, L_Pb_mean, phi_Pa_Mb_upr, col = alpha("red", 0.5))
  points(phi_Pa_Mb_mean ~ L_Pb_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
  text(phi_Pa_Mb_mean ~ L_Pb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
}

plot_fn2 = function(j) {
    # create the plots for both migratory strategies
  par(mgp = c(2, 0.35, 0), tcl = -0.15, mar = c(1,1,2,1))
  plot_fn(j = j, i = 1); if (j == 1) mtext(side = 2, line = 1.5, "Fall Migrants")
  plot_fn(j = j, i = 2); if (j == 1) mtext(side = 2, line = 1.5, "Spring Migrants")
}

par(mfcol = c(jags_data$ni,jags_data$nj), oma = c(2.5,3.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn2)
mtext(side = 1, line = 1.5, outer = T, "Parr Mean Length (mm)", cex = 1.2)
mtext(side = 2, line = 2, outer = T, "Overwinter Survival", cex = 1.2)
```

## Smolt Survival to LGR

>>>>

## Parr $\to$ Smolt Overwinter Survival {.tabset .tabset-pills}

### Time Series {.tabset .tabset-pills}

#### Fall Migrants {.tabset .tabset-pills}

##### Realized Alone

```{r phi_Pa_Mb_tseries-fall-1, fig.width = 6, fig.height = 5}
plot_f = function(j) {

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = ts_yrs, LH_type = i_fall, pop = j)), 
               main = pops[j], yrs = all_yrs[ts_yrs]
  )
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Overwinter Survival (Fall Migrants)")
```

##### Realized + Predicted

```{r phi_Pa_Mb_tseries-fall-2, fig.width = 6, fig.height = 5}
plot_f = function(j) {

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = ts_yrs, LH_type = i_fall, pop = j)), 
               main = pops[j], yrs = all_yrs[ts_yrs]
  )

  # add the predicted time series
  add_tseries(post_summ(post, sub_index("^phi_Pa_Mb_dot[year,LH_type,pop]", year = ts_yrs, LH_type = i_fall, pop = j)),
              yrs = all_yrs[t])

}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Overwinter Survival (Fall Migrants)")
```

#### Spring Migrants {.tabset .tabset-pills}

##### Realized Alone

```{r phi_Pa_Mb_tseries-spring-1, fig.width = 6, fig.height = 5}
plot_f = function(j) {

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = ts_yrs, LH_type = i_spring, pop = j)), 
               main = pops[j], yrs = all_yrs[ts_yrs]
  )
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Overwinter Survival (Spring Migrants)")
```

##### Realized + Predicted

```{r phi_Pa_Mb_tseries-spring-2, fig.width = 6, fig.height = 5}
plot_f = function(j) {

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^phi_Pa_Mb[year,LH_type,pop]", year = ts_yrs, LH_type = i_spring, pop = j)), 
               main = pops[j], yrs = all_yrs[ts_yrs]
  )

  # add the predicted time series
  add_tseries(post_summ(post, sub_index("^phi_Pa_Mb_dot[year,LH_type,pop]", year = ts_yrs, LH_type = i_spring, pop = j)),
              yrs = all_yrs[ts_yrs])

}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Overwinter Survival (Spring Migrants)")
```

### Mean Length Relationship {.tabset .tabset-pills}

```{r}
plot_f = function(j, i) {

@@

  # realized pairs
  segments(L_Pb_lwr, phi_Pa_Mb_mean, L_Pb_upr, phi_Pa_Mb_mean, col = alpha("red", 0.5))
  segments(L_Pb_mean, phi_Pa_Mb_lwr, L_Pb_mean, phi_Pa_Mb_upr, col = alpha("red", 0.5))
  points(phi_Pa_Mb_mean ~ L_Pb_mean, pch = 16, col = alpha("salmon", 0.5), cex = 1.8)
  text(phi_Pa_Mb_mean ~ L_Pb_mean, labels = substr(all_yrs[ts_yrs], 3, 4), cex = 0.65, col = "black")
}
```

#### Fall Migrants

```{r phi_Pa_Mb_fall_relationship, fig.width = 6, fig.height = 5}
par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f, i = 1)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Overwinter Survival (Fall Migrants)")
```

#### Spring Migrants

```{r phi_Pa_Mb_spring_relationship, fig.width = 6, fig.height = 5}
par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f, i = 2)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Overwinter Survival (Spring Migrants)")
```

## Smolt $\to$ LGR Survival {.tabset .tabset-pills}

### Time Series {.tabset .tabset-pills}

#### Realized Alone

```{r phi_Mb_Ma_tseries-1, fig.width = 6, fig.height = 5}
plot_f = function(j) {

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = ts_yrs, LH_type = i_spring, pop = j, origin = o_nor)), 
               main = pops[j], yrs = all_yrs[ts_yrs]
  )
}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Smolt to LGR Survival (NOR)")
```

#### Realized + Predicted

```{r phi_Mb_Ma_tseries-2, fig.width = 6, fig.height = 5}
plot_f = function(j) {

  # draw the realized time series
  plot_tseries(est = post_summ(post, sub_index("^phi_Mb_Ma[year,LH_type,origin,pop]", year = ts_yrs, LH_type = i_spring, pop = j, origin = o_nor)), 
               main = pops[j], yrs = all_yrs[ts_yrs]
  )

  # add the predicted time series
  add_tseries(post_summ(post, sub_index("^phi_Mb_Ma_dot[year,LH_type,origin,pop]", year = ts_yrs, LH_type = i_spring, pop = j, origin = o_nor)),
              yrs = all_yrs[ts_yrs])

}

par(mfrow = c(2,2), oma = c(1.5,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_f)
mtext(side = 1, outer = T, line = 0.25, "Brood Year")
mtext(side = 2, outer = T, line = 0.25, "Smolt to LGR Survival (NOR)")
```

### Mean Length Relationship
